Ecological network control

### 2018-04-19 publication/manuscript.Rmd
Add default parameters for R chunks

@@

```{r example_network, include = F}
loadd(example_net)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
options(xtable.comment = FALSE, 
        xtable.caption.placement = 'bottom',
        xtable.size = 'small',
        booktabs = TRUE)
```

@@

```{r example-network, include = F, eval = F}
loadd(example_net)
